### 2019-02-27 Sections/quality_of_service.tex

This no-go theorem does not apply if the initial states are non-Gaussian. One can also encode qubits using non-Gaussian continuous-variable states \cite{PhysRevA.64.012310}. Then error correction can be implemented using Gaussian operations, resulting in a Gaussian state. This protocol is known to be fault tolerant, however, the threshold requirements are quite stringent, such as needing the photon number in the squeezed state to be around 20 \cite{PhysRevA.73.012325}.

Another approach is to error correct on Gaussian states using non-Gaussian operations\cite{PhysRevA.67.062320}, similar to the entanglement distillation protocol. It is unclear which one is the most advantageous.

>>>>

This no-go theorem does not apply if the initial states are non-Gaussian. One can also encode qubits using non-Gaussian continuous-variable states \cite{bib:PhysRevA.64.012310}. Then error correction can be implemented using Gaussian operations, resulting in a Gaussian state. This protocol is known to be fault tolerant, however, the threshold requirements are quite stringent, such as needing the photon number in the squeezed state to be around 20 \cite{bib:PhysRevA.73.012325}.

Another approach is to error correct on Gaussian states using non-Gaussian operations. Such protocols have been proposed \cite{bib:PhysRevA.67.062320} and demonstrated \cite{bib:xiang2010heralded} for entanglement distillation. It has been shown that CV teleportation and distillation based on noiseless amplification can be combined to error correct Gaussian states against Gaussian noise \cite{bib:PhysRevA.84.022339}, implementable using linear optics and photon counting.
However, it is unclear whether such protocolsc can be made fault tolerant.
